How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

>>>>

In this paper, we have introduced a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow. The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies with statistical analysis across an ensemble of different initializations. By linking the governing Stokes equation to Darcy's law, we are able to extract porous media properties, like permeability, resistivity, tortuosity, and anisotropy, as they evolve over time. By comparing the resistivity to the directly computed drag, we find that these porous-media properties can be extracted with high accuracy.

	The ratio of longitudinal to transverse permeability provides the main
